---
title: "HW1"
author: "Muammer Dolmaci"
date: "5/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In the scope of Homework 1, three series will be analyzed from EVDS and compared with the search results via Google Trends.

## Libraries

```{r, echo=TRUE, eval=TRUE}
library(tidyverse)
#library(EVDS) #The API does not work properly
library(lubridate)
library(zoo)
library(readxl) #To read Excel file
library(ggplot2) #To plot the graphs
#library(dplyr)
```

## Data

Due to the API of EVDS does not work properly, the data of EVDS can be uploaded manually.

```{r, echo=TRUE, eval=TRUE}
#set_evds_key("UQ7bM51uXF") #ID if the API will start to work again

data <- read_excel("dataEVDS.xlsx")
View(data)

colnames(data) <- c("Date", "CarRentalExpenses", "GoldPrice", "ManufacturedCar")
str(data)
```

There are 3 different types of data sets in the Excel file. These are listed below.

**TP.KKHARTUT.KT2 -** The credit card expenses for car rental.

**TP.UR.S08 -** The number of manufactured car.

**TP.MK.KUL.YTL -** The sale price of gold. (TL/Gr)

## Plot

```{r, echo=TRUE, eval=FALSE}
plot <- ggplot(data, aes(x=Date, group=1))+
    geom_line(aes(y=CarRentalExpenses,color="blue"))+
  geom_line(aes(y=GoldPrice, color="red"))+
  geom_line(aes(y=ManufacturedCar, color="green"))+
  theme(panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle=90))+
   labs(x = "Date", y = "Rates", 
              title = "Car vs Gold Analysis")
plot
```


