---
title: "ETM58D HW3 HW4"
author: "Muammer Dolmaci"
date: "07/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In the scope of **ETM58D Homework 3 and 4**, the **electricity consumption of tomorrow** will be forecasted.


In the **Introdcution** section; the initial operations will be done and time-series will be plotted.

In the **Analysis** section; the tables, figures and predictions will be commented.

In the **Comparison** section; the obtained results will be compared.

In the **Conclusion** section; final results and comparisons will be commented.

# Introduction

## Libraries

All libraries that we used through the report is given below.

```{r, echo=TRUE, eval=TRUE}
library(readr)
library(ggplot2) 
library(MASS)
library(tidyverse)
library(dplyr)
library(lubridate)
library(glmnet)
```

## Data Import

The **Consumption Data** is imported via the code chunk below. 

The variable name of imported data is selected ``consumptionData`` and read the data from the csv file.

```{r, echo=TRUE, eval=TRUE}
consumptionData <- read_csv("GercekZamanliTuketim-01012016-31052021.csv")
str(consumptionData)
```

## Modifications

Some modification are done on the current data via the code chunks below.

```{r, echo=TRUE, eval=TRUE}
modifiedData <- mutate(consumptionData, date=dmy(Tarih), hour = as.character(Saat), hour = substring (hour, 1, 2))
```
  mutate(date = dmy(date),
         hour = as.character(hour),
         hour = substring(hour, 1, 2))




The **lag48** and **lag168** sets will be created for **total consumption** with their **errors**. Then they will be added to the ``updatedData`` as variables.

```{r, echo=TRUE, eval=TRUE}
lag48 <- lag(modifiedData, 48)
lag168 <- lag(modifiedData, 168)

updatedData <- mutate(modifiedData, 
                      lag48Tuketim=lag48$Tuketim, 
                      lag168Tuketim=lag168$Tuketim,
                      lag48Err=100*abs((lag48$Tuketim - modifiedData$Tuketim)/
                                    modifiedData$Tuketim),
                      lag168Err=100*abs((lag168$Tuketim - modifiedData$Tuketim)/
                                    modifiedData$Tuketim))
```

Data will be filtered according to the time interval as ``testPeriod``.

```{r, echo=TRUE, eval=TRUE}
testPeriod <- filter(updatedData, date>=as_date('2021-05-01'))
```

## Descriptive Analysis

**Descriptive Analysis** made by the code chunk below.

```{r, echo=TRUE, eval=TRUE}
summary(testPeriod$lag48Err)
summary(testPeriod$lag168Err)
quantile(testPeriod$lag48Err,probs = c(0,0.1,0.25,0.5,0.75,0.9))
quantile(testPeriod$lag168Err,probs = c(0,0.1,0.25,0.5,0.75,0.9))
cor(testPeriod$Tuketim,testPeriod$lag48Tuketim)
cor(testPeriod$Tuketim,testPeriod$lag168Tuketim)
```

Thanks to the correlation results, it is shown that lag168 fits better than lag48. So, **weekly seasonality** can be shown into the data.

## Graphs

The **graphs** of descriptive analysis summaries are plotted below.

```{r, echo=TRUE, eval=TRUE}
boxplot(testPeriod$lag48Err)
boxplot(testPeriod$lag168Err)
```

The **graph** of **Consumption** through the time is plotted below. 

```{r, echo=TRUE, eval=TRUE}
plot(updatedData$date, updatedData$Tuketim)
```

# Analysis

## Linear Regression

First of all, **Linear Regression** will be tried.

```{r, echo=TRUE, eval=TRUE}
linear_model <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data=testPeriod)
summary(linear_model)
```

According to the linear mode, the **prediction model** is prepared via the code chunk below.

```{r, echo=TRUE, eval=TRUE}
predicted_linear_model <- predict(linear_model, testPeriod)
```

**MAPE** values are calculated for **Linear Regression Prediction Model** to analyze the **accuracy**. 

MAPE values are also added to the ``testPeriod``.

```{r, echo=TRUE, eval=TRUE}
testPeriod <- mutate(testPeriod, linear_MAPE=100*(abs(testPeriod$Tuketim-predicted_linear_model)/testPeriod$Tuketim))
summary(testPeriod$linear_MAPE)
```

# Comparison

The Linear Regression model should be evaluated and established a model to forecast tomorrow.

The **Total Production Model** is established below for each hour seperately.

```{r, echo=TRUE, eval=TRUE}
modal_cons_h0 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "00"))
modal_cons_h1 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "01"))
modal_cons_h2 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "02"))
modal_cons_h3 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "03"))
modal_cons_h4 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "04"))
modal_cons_h5 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "05"))
modal_cons_h6 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "06"))
modal_cons_h7 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "07"))
modal_cons_h8 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "08"))
modal_cons_h9 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "09"))
modal_cons_h10 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "10"))
modal_cons_h11 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "11"))
modal_cons_h12 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "12"))
modal_cons_h13 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "13"))
modal_cons_h14 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "14"))
modal_cons_h15 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "15"))
modal_cons_h16 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "16"))
modal_cons_h17 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "17"))
modal_cons_h18 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "18"))
modal_cons_h19 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "19"))
modal_cons_h20 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "20"))
modal_cons_h21 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "21"))
modal_cons_h22 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "22"))
modal_cons_h23 <- lm(Tuketim ~ lag168Tuketim + lag48Tuketim, data = testPeriod %>% filter(hour == "23"))
```

Test sets are prepared below for each hour seperately, according to the model.

```{r, echo=TRUE, eval=TRUE}
test_set_h0 <- testPeriod %>% filter(hour == "00")
test_set_h1 <- testPeriod %>% filter(hour == "01")
test_set_h2 <- testPeriod %>% filter(hour == "02")
test_set_h3 <- testPeriod %>% filter(hour == "03")
test_set_h4 <- testPeriod %>% filter(hour == "04")
test_set_h5 <- testPeriod %>% filter(hour == "05")
test_set_h6 <- testPeriod %>% filter(hour == "06")
test_set_h7 <- testPeriod %>% filter(hour == "07")
test_set_h8 <- testPeriod %>% filter(hour == "08")
test_set_h9 <- testPeriod %>% filter(hour == "09")
test_set_h10 <- testPeriod %>% filter(hour == "10")
test_set_h11 <- testPeriod %>% filter(hour == "11")
test_set_h12 <- testPeriod %>% filter(hour == "12")
test_set_h13 <- testPeriod %>% filter(hour == "13")
test_set_h14 <- testPeriod %>% filter(hour == "14")
test_set_h15 <- testPeriod %>% filter(hour == "15")
test_set_h16 <- testPeriod %>% filter(hour == "16")
test_set_h17 <- testPeriod %>% filter(hour == "17")
test_set_h18 <- testPeriod %>% filter(hour == "18")
test_set_h19 <- testPeriod %>% filter(hour == "19")
test_set_h20 <- testPeriod %>% filter(hour == "10")
test_set_h21 <- testPeriod %>% filter(hour == "21")
test_set_h22 <- testPeriod %>% filter(hour == "22")
test_set_h23 <- testPeriod %>% filter(hour == "23")
```

Test predictions are prepared hour by hour below.

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h0 <- predict(modal_cons_h0, newdata = test_set_h0)
summary((abs(test_set_h0$Tuketim - test_set_pred_h0) / abs(test_set_h0$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h1 <- predict(modal_cons_h1, newdata = test_set_h1)
summary((abs(test_set_h1$Tuketim - test_set_pred_h1) / abs(test_set_h1$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h2 <- predict(modal_cons_h2, newdata = test_set_h2)
summary((abs(test_set_h2$Tuketim - test_set_pred_h2) / abs(test_set_h2$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h3 <- predict(modal_cons_h3, newdata = test_set_h3)
summary((abs(test_set_h3$Tuketim - test_set_pred_h3) / abs(test_set_h3$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h4 <- predict(modal_cons_h4, newdata = test_set_h4)
summary((abs(test_set_h4$Tuketim - test_set_pred_h4) / abs(test_set_h4$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h5 <- predict(modal_cons_h5, newdata = test_set_h5)
summary((abs(test_set_h5$Tuketim - test_set_pred_h5) / abs(test_set_h5$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h6 <- predict(modal_cons_h6, newdata = test_set_h6)
summary((abs(test_set_h6$Tuketim - test_set_pred_h6) / abs(test_set_h6$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h7 <- predict(modal_cons_h7, newdata = test_set_h7)
summary((abs(test_set_h7$Tuketim - test_set_pred_h7) / abs(test_set_h7$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h8 <- predict(modal_cons_h8, newdata = test_set_h8)
summary((abs(test_set_h8$Tuketim - test_set_pred_h8) / abs(test_set_h8$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h9 <- predict(modal_cons_h9, newdata = test_set_h9)
summary((abs(test_set_h9$Tuketim - test_set_pred_h9) / abs(test_set_h9$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h10 <- predict(modal_cons_h10, newdata = test_set_h10)
summary((abs(test_set_h10$Tuketim - test_set_pred_h10) / abs(test_set_h10$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h11 <- predict(modal_cons_h11, newdata = test_set_h11)
summary((abs(test_set_h11$Tuketim - test_set_pred_h11) / abs(test_set_h11$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h12 <- predict(modal_cons_h12, newdata = test_set_h12)
summary((abs(test_set_h12$Tuketim - test_set_pred_h12) / abs(test_set_h12$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h13 <- predict(modal_cons_h13, newdata = test_set_h13)
summary((abs(test_set_h13$Tuketim - test_set_pred_h13) / abs(test_set_h13$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h14 <- predict(modal_cons_h14, newdata = test_set_h14)
summary((abs(test_set_h14$Tuketim - test_set_pred_h14) / abs(test_set_h14$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h15 <- predict(modal_cons_h15, newdata = test_set_h15)
summary((abs(test_set_h15$Tuketim - test_set_pred_h15) / abs(test_set_h15$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h16 <- predict(modal_cons_h16, newdata = test_set_h16)
summary((abs(test_set_h16$Tuketim - test_set_pred_h16) / abs(test_set_h16$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h17 <- predict(modal_cons_h17, newdata = test_set_h17)
summary((abs(test_set_h17$Tuketim - test_set_pred_h17) / abs(test_set_h17$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h18 <- predict(modal_cons_h18, newdata = test_set_h18)
summary((abs(test_set_h18$Tuketim - test_set_pred_h18) / abs(test_set_h18$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h19 <- predict(modal_cons_h19, newdata = test_set_h19)
summary((abs(test_set_h19$Tuketim - test_set_pred_h19) / abs(test_set_h19$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h20 <- predict(modal_cons_h20, newdata = test_set_h20)
summary((abs(test_set_h20$Tuketim - test_set_pred_h20) / abs(test_set_h20$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h21 <- predict(modal_cons_h21, newdata = test_set_h21)
summary((abs(test_set_h21$Tuketim - test_set_pred_h21) / abs(test_set_h21$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h22 <- predict(modal_cons_h22, newdata = test_set_h22)
summary((abs(test_set_h22$Tuketim - test_set_pred_h22) / abs(test_set_h22$Tuketim)) * 100)
```

```{r, echo=TRUE, eval=TRUE}
test_set_pred_h23 <- predict(modal_cons_h23, newdata = test_set_h23)
summary((abs(test_set_h23$Tuketim - test_set_pred_h23) / abs(test_set_h23$Tuketim)) * 100)
```

# Conclusion

In conclusion, according to the previous consumption data, we obtained a set of prediction for the day of *d+1*. This prediction includes not only the mean value but also the min and max predictions thanks to the linear regression.
